---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    fig.path = "man/figures/README-",
    out.width = "100%"
)
```

# PloidyAssignR
PloidyAssignR is a computational framework that allows automated ploidy assignment from Strand-seq libraries. The tool observes ploidy-dependent strand state distribution patterns and optimizes kmeans clustering to assign the respective ploidy state. 

<!-- badges: start -->
<!-- badges: end -->


## Installation

You can install PloidyAssignR via terminal from Gitlab EMBL

```
cd path/to/your/desired/directory
git clone https://git.embl.de/christia/ploidyassignr.git
```

### Loading PloidyAssignR

Open Rstudio and create a Rproject in the directory containing the git repository you just cloned.
PloidyAssignR is still in development and has not yet been deployed. Therefore library() does not work and you need to load the package via devtools.

```{r}
if (!requireNamespace("devtools")) {
    install.packages("devtools")
}

devtools::load_all()
```

Now PloidyAssignR is loaded and you can use its functions etc.

## How to Use PloidyAssignR
Please refer to the vignette to learn about PloidyAssignR's functionality.
```{r, eval=FALSE}
browseVignettes("PloidyAssignR")
```


The package contains a Rshiny app to help inspect your ploidy analysis data sets. To get a quick overview consider watching: https://drive.google.com/file/d/1y56aibBt9mg97K1fT2-SKESm3Zp0GODe/view?usp=sharing 

To launch the app run:

```{r, eval=FALSE}
run_app()
```




